---
title: "A (very) short introduction to R"
author: "許sir"

---

### **設定工作區**
```{r message=FALSE, warning=FALSE, results='hide'}
setwd("D:/Rdata Practice/R BasicLab")

```


### **ToDo 1**
Compute the dierence between 2014 and the year you started at this university and divide this by the dierence between 2014 and the year you were born. Multiply this with 100 to get the percentage of your life you have spent at this university. Use brackets if you need them.

```{r message=FALSE, warning=FALSE}
(x<-(2014-2010)/(2014-1992)*100)
```


### **ToDo 2**
Repeat the previous ToDo, but with several steps in between. You can give the variables
any name you want, but the name has to start with a letter.
```{r message=FALSE, warning=FALSE}
(x1<-(2014-2010)/(2014-1992)*100)
(a1<-(2014-2010)/(2014-1992)*100)
```


### **ToDo 3**
Compute the sum of 4, 5, 8 and 11 by first com-bining them into a vector and then using the
function sum.
```{r message=FALSE, warning=FALSE}
t3<-c(4,5,8,11)
sum(t3)
```


### **ToDo 4**
Plot 100 normal random numbers.
```{r message=FALSE, warning=FALSE}
t4<-rnorm(100,0,1)
plot(t4,main="ToDo4")
```


### **ToDo 5**
Find help for the sqrt function.
```{r message=FALSE, warning=FALSE}
?sqrt
```


### **ToDo 6**
Make a file called "firstscript.R" containing R-code that generates 100 random numbers and
plots them, and run this script several times.
```{r message=FALSE, warning=FALSE}

# firstscript.R 內的程式碼如下
# x=rnorm(100);plot(x)

source("firstscript.R") # 因為已經設定工作區了，所以會自動抓取
```


### **ToDo 7**
Put the numbers 31 to 60 in a vector named P and in a matrix with 6 rows and 5 columns
named Q. Tip: use the function seq. Look at the different ways scalars, vectors and matrices
are denoted in the workspace window.
```{r message=FALSE, warning=FALSE}
p = 31:60
#Q = matrix(data=p, nrow = 6)
Q<-matrix(data=p,6,5)
Q
```


### **ToDo 8**
Make a script file which constructs three ran-dom normal vectors of length 100. Call these
vectors x1, x2 and x3. Make a data frame called t with three columns (called a, b and c) con-taining respectively x1, x1+x2 and x1+x2+x3.
Call the following functions for this data frame:plot(t) and sd(t). Can you understand the
results? Rerun this script a few times.
```{r message=FALSE, warning=FALSE}
x1 = rnorm(100)
x2 = rnorm(100)
x3 = rnorm(100)
t = data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
plot(t)
sd(as.numeric(unlist(t)))
```


### **ToDo 9**
Add these lines to the script file of the previous section. Try to find out, either by experiment-ing or by using the help, what the meaning is of rgb, the last argument of rgb, lwd, pch, cex.
```{r message=FALSE, warning=FALSE}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,1,0,0.7))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=22, cex=2,col=rgb(0,0,1,0.3))
?rgb
```


### **ToDo 10**
Make a file called tst1.txt in Notepad from the example in Figure 4 and store it in your
working directory. Write a script to read it, to multiply the column called g by 5 and to store it as tst2.txt.
```{r message=FALSE, warning=FALSE}
d<-data.frame(a=c(3,4,5),b=c(12,43,54))
write.table(d,file="tst0.txt",row.names=FALSE)
d1<-data.frame(a=c(1,2,4,8,16,32),g=c(2,4,8,16,32,64),x=c(3,6,12,24,48,96))
write.table(d1,file="tst1.txt",row.names=FALSE)
d3<-read.table("tst1.txt",header=TRUE)
(d4<-d3*matrix(c(1,1,1,1,1,1,5,5,5,5,5,5,1,1,1,1,1,1)))
write.table(d4,file="tst2.txt",row.names=FALSE)
```


### **ToDo 11**
Compute the mean of the square root of a vector of 100 random numbers. What happens?
```{r message=FALSE, warning=FALSE}
t11<-rnorm(100)
mean(sqrt(t11))

#?root
```

### **ToDo 12**
Make a graph with on the x-axis: today, Sin-terklaas 2014 and your next birthday and on
the y-axis the number of presents you expect on each of these days. Tip: make two vectors first.
```{r message=FALSE, warning=FALSE}
data1 = c(strptime(c("20141121","20151121"),format="%Y%m%d"))
data2 = c(100,90)
plot(data1,data2, xlab = "Date",ylab="Count",main = "The number of presents I expected.")
```


### **ToDo 13**
Make a vector from 1 to 100. Make a for-loop which runs through the whole vector. Multiply
the elements which are smaller than 5 and larger than 90 with 10 and the other elements with 0.1.
```{r message=FALSE, warning=FALSE}
s = 1:100
for(i in 1:100)
{
  if (s[i] < 5 | s[i] > 90)
  {
    s[i] = s[i] * 10
  } else
  {
    s[i] = s[i] * 0.1
  }
}
s
```


### **ToDo 14**
Write a function for the previous ToDo, so that you can feed it any vector you like
(as argument). Use a for-loop in the func-tion to do the computation with each ele-
ment. Use the standard R function length in the specification of the counter.
```{r message=FALSE, warning=FALSE}
k=1:10
fun = function(arg1)
{
  l = length(arg1)
  for(i in 1:l)
  {
    if (arg1[i] < 5 | arg1[i] > 90)
    {
      arg1[i] = arg1[i] * 10
    } else
    {
      arg1[i] = arg1[i] * 0.1
    }
  }
  return (arg1)
}
fun(arg1=k)
```

